Age-related changes in plant growth and traits

### 2016-11-15 scripts/tests.Rmd
code for file testing R issues

repro4 <- select(SummaryInd,individual,seed_count,repro_inv,species)
repro4 <- merge(repro4,repro3,by="individual")
plot(weight ~ repro_inv,repro4,col=col.spp(species),pch=16,log="xy")
abline(0,1)

@@

>>>>

SummaryInd$repro_new <- SummaryInd$prepollen2_all_inv + SummaryInd$postpollen2_all_inv
repro4 <- select(SummaryInd,individual,seed_count,repro_inv,repro_new, species)
repro4 <- merge(repro4,repro3,by="individual")
plot(weight ~ repro_new,repro4,col=col.spp(species),pch=16,log="xy")
abline(0,1)

@@

check2 <- subset(InvestmentByPart,species=="BOLE"&(part=="late_flower_petals"|part=="flower_petals"))

repro3 <- check2 %>%
    group_by(individual) %>%
    summarise_each(funs(sum), count)

check <- subset(SummaryInd,species=="BOLE")
check <- select(check,individual, postpollen_count,prepollen_count_reach_flowering,seed_count)
check3 <- merge(check,repro3,by="individual")
